### 2019-11-22 4_metg.tex
Fiddle with figure placement.
Update to METG section.

Given that Task Bench permits the rapid exploration of a large space
of application scenarios, one question is how to characterize the
overall performance of the programming systems under study. As noted
earlier, the overheads of the systems we consider varies by more than
five orders of magnitude. This makes it challenging to extract useful
information from weak and strong scaling runs.

@@

We introduce \emph{minimum effective task granularity}, or METG, an
efficiency-constrained metric for runtime-limited
performance. METG(50\%) for an application $A$ is
the smallest average task granularity (i.e., task duration) such that $A$
achieves overall efficiency of at least 50\%. For example, in
compute-bound applications efficiency can be measured as the
percentage of the available FLOP/s achieved. On Cori with 1.26 TFLOP/s available per Haswell node, METG(50\%) corresponds to
the smallest task granularity achieved while maintaining at least 0.63
TFLOP/s per node. For applications not amenable to being characterized by raw FLOP/s or B/s, an application-specific measure of performance can be
used instead (e.g., mesh cells processed per second).

@@

To calculate METG, the data is replotted along axes of efficiency
(i.e., as a percentage of the peak FLOP/s achieved) and task
granularity (i.e., $\text{wall time} \times \text{num.~cores}/\text{num.~tasks}$), as shown in Figure~\ref{fig:efficiency-mpi}. Note that a \emph{task} is defined
broadly to be any continuously-executing unit of application code,
and thus it makes sense to discuss tasks even in systems
with no explicit notion of tasking, such as in MPI programs written in a bulk synchronous style. In this case, the tasks run a
compute-bound kernel included in the Task Bench implementation,
described in more detail in Section~\ref{sec:task-bench}.

>>>>

Given that Task Bench permits the rapid exploration of a large space
of application scenarios, one question is how to characterize the
performance and efficiency of the systems under study. As noted
earlier, the overheads of the systems we consider varies by more than
five orders of magnitude. This makes it challenging to extract useful
information from weak and strong scaling runs.

@@

We introduce \emph{minimum effective task granularity}, or METG, an
efficiency-constrained metric for runtime-limited
performance. METG(50\%) for an application $A$ is
the smallest average task granularity (i.e., task duration) such that $A$
achieves overall efficiency of at least 50\%. Note that METG is parameterized by the efficiency metric. For example, in
compute-bound applications efficiency can be measured as the
percentage of the available FLOP/s achieved. On Cori with 1.26 TFLOP/s available per Haswell node, METG(50\%) corresponds to
the smallest task granularity achieved while maintaining at least 0.63
TFLOP/s per node. However, METG is not tied to peak performance, and
in applications not amenable to being characterized in this way,
another application-specific measure of performance can be used. For
example, a simulation on a mesh might use the number of mesh cells
processed per second (i.e., total number of cells divided by wall
clock time per iteration of the main simulation loop).

The choice of 50\% is also a parameter and is not fundamental to
METG. We use 50\% in our studies in order to avoid certain pathologies
associated with lower efficiency thresholds (see
Section~\ref{subsec:peak-performance-and-efficiency}), and also
because it aligns with what we observe in practice. For example, in a
CSCS application for new projects, users are instructed to "select the
most parallel efficient job size (ratio of benchmark speed-up
vs. linear speed-up above 50\%)" \cite{CSCSReport}. This corresponds
to METG(50\%).

@@

To calculate METG, the data is replotted along axes of efficiency
(i.e., as a percentage of the peak FLOP/s achieved) and task
granularity (i.e., $\text{wall time} \times \text{num.~cores}/\text{num.~tasks}$), as shown in Figure~\ref{fig:efficiency-mpi}. Note that a \emph{task} is defined
broadly to be any continuously-executing unit of application code,
and thus it makes sense to discuss tasks even in systems
with no explicit notion of tasking, such as MPI. In this case, the
tasks run the compute-bound kernel shown in
Section~\ref{sec:task-bench}.
